---
title: "Boston Crime Map"
author: "Michael Sauter"
date: "5-AUG-2018"
output: 
  html_document: 
    keep_md: yes
---

The data for this map is taken from the Boston Crime dataset started in 2015.The lots of datasets for Boston are available here: https://data.boston.gov/dataset


## Introduction

This project was created as part of the Developing Data Products course of the Coursera [Data Science Specialisation](https://www.coursera.org/specializations/jhu-data-science). The goal of the project is to create a web page using R Markdown that features a map created with Leaflet, and to host the resulting web page on either GitHub Pages, RPubs, or NeoCities.

## Map of passenger traffic

The following map represents reported crimes in Boston since 2015.It even shows some mis reported location in the Atlantic next to central Africa.

## Reading Data

Reading data from csv file in home directory, column 4 and 5, and subsetting to extract 1000 random sample.  

```{r, echo=TRUE, results=FALSE}
data <- "bostoncrime.csv"
df <- read.csv(data              )
df <- df[sample(nrow(df), 1000), c(4,5)]

```
 

## Plotting Map

The map below shows a clustered view of all the spots where crimes were recorded in Boston since 2015. 

```{r Leaflet, echo=TRUE}
library(leaflet)

df %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(clusterOptions = markerClusterOptions())

```
